Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-05-25 doc/paper.Rmd
justify omitting 10-ha plots

In 1997--1998 we established a series of 5000 m^2^ plots ($50 \times 100$m) in the BDFFP reserves in which we marked and measured all *Heliconia acuminata*.
The plots are located in continuous forest ($n=6$), 10 ha fragments ($n=3$), and 1-ha fragments ($n=4$), with distance between plots ranging from 500 m--41 km.
Plots in 1-ha fragments were on one randomly selected half of the fragment, plots in 10 ha fragments were in the fragment center, and plots in continuous forest were placed in locations 500--4000 m from the borders of secondary and mature forest.
This study uses data from 1-ha fragments and continuous forest sites.
<!--# maria: justify why 10ha plots omitted or don't say they exist -->

>>>>

In 1997--1998 we established a series of 5000 m^2^ plots ($50 \times 100$m) in the BDFFP reserves in which we marked and measured all *Heliconia acuminata*.
The plots are located in continuous forest ($n=6$), 10 ha fragments ($n=3$), and 1-ha fragments ($n=4$), with distance between plots ranging from 500 m--41 km.
Plots in 1-ha fragments were on one randomly selected half of the fragment, plots in 10 ha fragments were in the fragment center, and plots in continuous forest were placed in locations 500--4000 m from the borders of secondary and mature forest.
This study uses data only from 1-ha fragments and continuous forest sites because these represent extremes and because there are only three 10 ha fragment plots.
